---
title: "W_UP_01"
author: "Jayline Zelaya"
date: "fall 2023"
output: html_document
---

  

The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Is there a difference in the average number of push-ups a linebacker and skill player can do in two minutes?

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

push-up is a numeric variable, position is a categorical. Therefore we use cat.rmd

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results
 
<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results
This table shows the average number of push-ups for the line players was 17, while the average for skill players was 50.
### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position, data=mydata)
```
This box-plot shows that the skill players do more push-ups in 2 minutes on average than line players.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups ~ position, data=mydata)
```
This table shows that the average number of push-ups for a line player was 17, while the average for a skill player was 50.

## Inferential Results

```{r}
t.test(pushups~position, data=mydata)
```
p value is less than 0.05 so we reject the null hypothesis and conclude there is a difference between the amount of push-ups a line pkayer and skill player can do in 2 minutes.

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was is there a difference in the average number of push-ups that a line player can do against a skill player in 2 minutes? We have concluded, there is a difference between whether or not the players can do more push-ups than each other in 2 minutes. In fact, skill players can do more push-ups. Line players can do an average of 17 push-ups in 2 minutes. While on the other hand, skill players can do an average of 50 push-ups in 2 minutes.
